---
title: "Olney Corridor Analysis"
author: "Zoe Yoo"
date: "11/10/2021"
output: 
  html_document: 
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)

source("../code/segmentation_code.R")

library(tinytex)
library(tidyverse); library(tidycensus)
library(reactable) ; library(shiny)
library(sf) ; library(sp)
library(tidyverse)
library(rgeos)
library(xlsx)
library(kableExtra)
library(rphl) 
library(viridis)
library(gridExtra)
library(scales)
library(leaflet)
library(leaflet.mapboxgl)
library(leaflet.extras)

options(tigris_class = "sf") # tells tidycensus to download Census geometries in the sf or Simple Feature format

import_apc <- function() {
  #apc_trip_data <- read_feather("./data/preped_apc_data.feather")
  apc_trip_data <- read.csv("../data/combined_apc_dataset.csv") %>% 
    mutate(stop_id = paste0(agency_id, stop_id))
  
  output <- apc_trip_data %>% adjust_dwell_and_velo()
  
  return(output)
}

apc_data <- import_apc()

```

```{r functions, include=FALSE, message=FALSE}

find_trip_dat_v2 <- function(apc_trip_data, stop_list) {
  
  filtered_dat <- filter_trip_list(apc_trip_data, stop_list)
  nested_trip_dat <- nest_trip_data_v2(filtered_dat)
  print(paste("Running passenger data for", count(nested_trip_dat %>% as_tibble()), "trips", sep = " "))
  
  final_dat <- lazy_dt(run_passenger_data_v3(nested_trip_dat, stop_list)) %>%
    ungroup()  %>%
    lazy_dt() %>%
    dt_unnest(calculated_pass) %>% # got rid of na_if(0) %>% 
    as_tibble()
  gc()
  return(final_dat)
}

speed_by_route_dir_plot <- function(hourly_route_direction_analytics) {
  p<- ggplot(hourly_route_direction_analytics, aes(x = trip_hour, y = avg_segment_speed, color=direction_id)) + 
        geom_line() +
        geom_point(size=1.5) + 
        #scale_color_viridis(discrete = TRUE) +
        scale_y_continuous(name = "Speed (MPH) - Includes Dwell Time", n.breaks = 8) +
        scale_x_continuous(name = "Hour", breaks = c(0:23)) +
        labs(title = "Hourly Speed by Route/Direction") +
        theme(text = element_text(size = 9)) +
        facet_wrap(~route_id, ncol = 2) + 
        theme(text = element_text(size = 9)) +
        theme(axis.text.x = element_text(angle = 90))
  return(p)
}


ridership_by_route_dir_plot <- function(hourly_route_direction_analytics) {
    p <- ggplot(hourly_route_direction_analytics, aes(x = trip_hour, y = daily_ridership, fill=direction_id)) + 
        geom_bar(position = "stack", stat = "identity") +
        #geom_point(size=3) + 
        #scale_color_viridis(discrete = TRUE) +
        scale_y_continuous(name = "Riders Served", n.breaks = 8) +
        scale_x_continuous(name = "Hour", breaks = c(0:23)) +
        labs(title = "Hourly Ridership by Route/Direction") +
        theme(text = element_text(size = 9)) +
        facet_wrap(~route_id, ncol = 2) + 
        theme(text = element_text(size = 9))  +
        theme(axis.text.x = element_text(angle = 90))
    return(p)
}

```


## Overall Corridor Analysis

### Broad Descriptive Stats

* Info on the corridor, which bus routes run through it (18,26), the neighborhood around it, basic population?
Factors we have: average segment speed, stop spacing (avg_stop_spacing_ft), ons/offs, average load, max entry load (max # of people on first? load), dwell time
* Map of corridor? Automated using leaflet? maybe kind of tricky
* Could use tidycensus to pull in basic descriptive info on the corridor

```{r}

stop_list <- I(list(c("SEPTA372","SEPTA15911","SEPTA15794", "SEPTA15912", "SEPTA15789", "SEPTA15915", "SEPTA15586", "SEPTA15793", "SEPTA15913","SEPTA15791", "SEPTA15914", "SEPTA15792", "SEPTA15786", "SEPTA15916", "SEPTA15782", "SEPTA15917", "SEPTA15587", "SEPTA16979", "SEPTA15779", "SEPTA15918", "SEPTA15919"),c("SEPTA15796", "SEPTA15908", "SEPTA15798", "SEPTA15907", "SEPTA15799", "SEPTA28699", "SEPTA15800", "SEPTA16966", "SEPTA15814", "SEPTA16965", "SEPTA381", "SEPTA15795", "SEPTA373", "SEPTA15910"),c("SEPTA16963", "SEPTA15815", "SEPTA16964", "SEPTA15817","SEPTA15819", "SEPTA16961", "SEPTA32312", "SEPTA16960", "SEPTA15820", "SEPTA16959", "SEPTA15822", "SEPTA15697", "SEPTA15899", "SEPTA15818", "SEPTA16962")))
subcorridor_name <- c("Olney and Chelten - Olney and Broad", "Olney and Broad - Olney and 7th", "Olney and 7th - Olney and Front")
subcorridor_id <- c("CB","B7","7F")
subcorridors <- data.frame(subcorridor_id,subcorridor_name,stop_list)

stop_list <- unlist(stop_list)

#create_stops()
stops_w_ridership <- st_read("../data/stops_ridership.geojson") %>% 
    mutate_if(is.factor, as.character) %>% 
    mutate(route_list = as.list(strsplit(as.character(route_str), ",")))
#create_routes()
routes_w_ridership <- st_read("../data/routes_ridership.geojson") %>% 
    mutate_if(is.factor, as.character)
# import links
links <- st_read("../data/links_with_stops.geojson") 
link_stop_data <- links %>% mutate(fromto = as.character(fromto), secondLocationID = as.character(secondLocationID)) %>% 
    mutate(stop_list = as.list(strsplit(as.character(stop_str), ","))) 
# import APC data
apc_data <- read.csv("../data/combined_apc_dataset.csv") %>%  
    mutate(stop_id = paste0(agency_id, stop_id)) %>% 
    mutate(dwell_time = case_when(
        agency_id == "NJT" ~ dwell_time * 60,
        TRUE ~ dwell_time
    ))
apc_data <- adjust_dwell_and_velo(apc_data)

alltracts <- st_read("https://opendata.arcgis.com/datasets/8bc0786524a4486bb3cf0f9862ad0fbf_0.geojson")
#restrict to just tracts that stops are in


#pulling the acs data
acs_trans <- c("B08301_001", #workers
              "B08301_002", #means of transportation to work: car
              "B08301_003", #means of transportation to work: car, drove alone
              "B08301_010", #means of transportation to work: public transit
              "B08301_011", #means of transportation to work: public transit, bus
              "B08301_012", #means of transportation to work: public transit, subway
              "B08301_013", #means of transportation to work: public transit, commuter rail
              "B08301_014", #means of transportation to work: public transit, light rail/trolley
              "B08301_016", #means of transportation to work: taxicab
              "B08301_018", #means of transportation to work: bicycle
              "B08301_019", #means of transportation to work: walked
              "B08301_021" #means of transportation to work: wfh
              )

trip_dat <- (find_trip_dat_v2(apc_data, stop_list))

analytics <- analyze_segment(trip_dat)
route_analytics <- analyze_segment_route(trip_dat)
binned_analytics <- suppressWarnings(analyze_segment_hourbin(trip_dat))
hourly_analytics <- suppressWarnings(analyze_segment_hourly(trip_dat))
hourly_route_analytics <- suppressWarnings(analyze_segment_route_hourly(trip_dat))
hourly_route_direction_analytics <- suppressWarnings(analyze_segment_route_direction_hourly(trip_dat))


```

```{r}

routes <- subset(routes_w_ridership, routes_w_ridership$Route %in% trip_dat$route_id)

# map of routes that exist in this corridor
# leaflet() %>% 
#   setView(lng = -75.164012, lat = 39.952533, zoom = 12) %>% 
#   addProviderTiles(providers$Stamen.Toner) %>% 
#   addPolylines(data = routes, color = "#4377bc", weight = 4, layerId = link_stop_data$fromto, opacity = 0.5)
```

### Corridor Level Descriptive Stats

```{r}

table_1 <- route_analytics %>% bind_rows(analytics %>% mutate(route_id = "Total"))
 
kable(table_1, booktabs = TRUE, align = 'c') %>%
  kable_styling(latex_options = "scale_down")  %>%
  row_spec(dim(table_1)[1], bold = T) %>% # format last row
  column_spec(1, italic = T) %>%  # format first column
  scroll_box(width = "100%", height = "300px")

ggplot(route_analytics, aes(x = route_id, y = avg_segment_speed)) + 
  geom_bar(stat = "identity", fill="skyblue", alpha=0.7) +
  geom_errorbar(data = route_analytics, stat = "identity", ymin = route_analytics$avg_speed_10_pct, ymax = route_analytics$avg_speed_90_pct, colour="orange", alpha=0.6, size=1.3, width = 0.4) + 
  scale_y_continuous(name = "Speed (MPH) - Includes Dwell Time", n.breaks = 8, limits = c(0, max(route_analytics$avg_speed_90_pct) * 1.1)) +
  scale_x_discrete(name = "Route Number") + 
  labs(title = paste0("The Average Bus Travels at ", round(mean(analytics$avg_segment_speed), 1), " MPH on the Corridor")) +
  theme(text = element_text(size = 9))

ggplot(binned_analytics, aes(x = timeframe, y = daily_ridership, label = daily_ridership)) + 
  geom_bar(stat = "identity", fill="skyblue", alpha=0.7) +
  geom_text(position=position_dodge(width=0.9), vjust = -0.75, size = 3) +
  scale_y_continuous(name = "Total Riders Served", n.breaks = 5) + #, limits = c(0, max(binned_analytics$avg_speed_90_pct) * 1.1)) +
  scale_x_discrete(name = element_blank()) +
  labs(title = "Ridership by Period (All Routes)")+
  theme(text = element_text(size = 9))

ggplot(binned_analytics, aes(x = timeframe, y = avg_segment_speed)) + 
  geom_bar(stat = "identity", fill="skyblue", alpha=0.7) +
  geom_errorbar(data = binned_analytics, stat = "identity", ymin = binned_analytics$avg_speed_10_pct, ymax = binned_analytics$avg_speed_90_pct, colour="orange", alpha=0.6, size=1.3, width = 0.4) + 
  scale_y_continuous(name = "Speed (MPH) - Includes Dwell Time", n.breaks = 8, limits = c(0, max(binned_analytics$avg_speed_90_pct) * 1.1)) +
  scale_x_discrete(name = element_blank()) +
  labs(title = "Speed by Period (All Routes)")+
  theme(text = element_text(size = 9))

ggplot(hourly_analytics) + 
  geom_line(aes(x = trip_hour, y = avg_segment_speed)) +
  geom_point(aes(x = trip_hour, y = avg_segment_speed), shape=21, size=3) + 
  scale_y_continuous(name = "Speed (MPH) - Includes Dwell Time", n.breaks = 8) +
  scale_x_continuous(name = "Hour", breaks = c(0:23)) +
  labs(title = "Hourly Speed (All Routes)")+
  theme(text = element_text(size = 9))

```


### Corridor/Route Level Stats

```{r}
grid.arrange(ncol=2,
ggplot(route_analytics, aes(y = daily_ridership, x = route_id, label = daily_ridership)) + 
  geom_bar(stat = "identity", fill = "skyblue") +
  geom_text(position=position_dodge(width=0.9), vjust = -0.75, size = 3) +
  scale_y_continuous(name = "Total Riders Served", n.breaks = 8, limits = c(0, max(route_analytics$daily_ridership) * 1.1)) + 
  scale_x_discrete(name = "Route Number") + 
  labs(title = paste0("The Corridor Serves ", round(sum(analytics$daily_ridership)), " Riders per Day")) +
  theme(text = element_text(size = 9)),
ggplot(route_analytics, aes(x=route_id, y = trips, label = trips)) + 
  geom_bar(position="dodge", stat="identity") + 
  geom_text(position=position_dodge(width=0.9), vjust = -0.75, size = 3) +
  ylab("Daily Trips (2019)") + 
  scale_x_discrete(name = "Route Number") + 
  scale_fill_phl(palette = "main", discrete = T) +
  labs(fill= "", title = paste0("The Corridor Serves ", sum(route_analytics$trips, na.rm = TRUE), " Trips per Day")) + 
  #theme_phl() + 
  theme(legend.position = "top")+
  theme(text = element_text(size = 9))
)

ggplot(route_analytics, aes(x=route_id, y = service_hours, label = round(service_hours))) + 
  geom_bar(position="dodge", stat="identity") + 
  geom_text(position = "dodge", stat = "identity", vjust = -0.75) +
  #ggtitle("Market and JFK serve over 1,100 Bus Trips per Day") + 
  ylab("Service Hours Per Day") + 
  scale_x_discrete(name = "Route Number") + 
  scale_fill_phl(palette = "main", discrete = T) +
  labs(fill= "", title = paste0("The Corridor Serves ", round(sum(route_analytics$service_hours, na.rm = TRUE), 1), " Service Hours per Day")) + 
  #theme_phl() + 
  theme(legend.position = "top")+
  theme(text = element_text(size = 9))

ggplot(hourly_route_analytics, aes(x = trip_hour, y = daily_ridership, group=route_id, fill=route_id)) + 
  geom_bar(position = "stack", stat = "identity") +
  #geom_point(shape=21, size=3) + 
  scale_color_viridis(discrete = TRUE) +
  scale_y_continuous(name = "Riders Served", n.breaks = 8) +
  scale_x_continuous(name = "Hour", breaks = c(0:23)) +
  labs(title = "Hourly Ridership by Route (all directions)") +
  theme(text = element_text(size = 9))

speed_by_route_dir_plot(hourly_route_direction_analytics)
ridership_by_route_dir_plot(hourly_route_direction_analytics)

ggplot(hourly_route_direction_analytics, aes(x = trip_hour, y = avg_run, fill=direction_id)) + 
  geom_bar(position = "stack", stat = "identity") +
  #geom_point(size=3) + 
  #scale_color_viridis(discrete = TRUE) +
  ylab("Average Running Time (Includes Dwell)") +
  scale_x_continuous(name = "Hour", breaks = c(0:23)) +
  labs(title = "Average Corridor Running Time by Route/Direction") +
  theme(text = element_text(size = 9)) +
  facet_wrap(~route_id + direction_id, ncol = 2) + 
  theme(text = element_text(size = 9))  +
  theme(axis.text.x = element_text(angle = 90))

```



## Sub-Corridor Analysis


### Chelten to Broad

```{r}


stop_cb <- c("SEPTA372","SEPTA15911","SEPTA15794", "SEPTA15912", "SEPTA15789", "SEPTA15915", "SEPTA15586", "SEPTA15793", "SEPTA15913","SEPTA15791", "SEPTA15914", "SEPTA15792", "SEPTA15786", "SEPTA15916", "SEPTA15782", "SEPTA15917", "SEPTA15587", "SEPTA16979", "SEPTA15779", "SEPTA15918", "SEPTA15919")

trip_dat_cb <- (find_trip_dat_v2(apc_data, stop_cb))

analytics_cb <-   analyze_segment(trip_dat_cb)
route_analytics_cb <- analyze_segment_route(trip_dat_cb)
binned_analytics_cb <- suppressWarnings(analyze_segment_hourbin(trip_dat_cb))
hourly_analytics_cb <- suppressWarnings(analyze_segment_hourly(trip_dat_cb))
hourly_route_analytics_cb <- suppressWarnings(analyze_segment_route_hourly(trip_dat_cb))
hourly_route_direction_analytics_cb <- suppressWarnings(analyze_segment_route_direction_hourly(trip_dat_cb))


p <- ggplot(route_analytics_cb, aes(y = daily_ridership, x = route_id, label = daily_ridership)) + 
  geom_bar(stat = "identity", fill = "skyblue") +
  geom_text(position=position_dodge(width=0.9), vjust = -0.75, size = 3) +
  scale_y_continuous(name = "Total Riders Served", n.breaks = 8, limits = c(0, max(route_analytics$daily_ridership) * 1.1)) + 
  scale_x_discrete(name = "Route Number") + 
  labs(title = paste0("The Corridor Serves ", round(sum(analytics$daily_ridership)), " Riders per Day")) +
  theme(text = element_text(size = 9))

ggplot(hourly_analytics_cb) + 
  geom_line(aes(x = trip_hour, y = avg_segment_speed)) +
  geom_point(aes(x = trip_hour, y = avg_segment_speed), shape=21, size=3) + 
  scale_y_continuous(name = "Speed (MPH) - Includes Dwell Time", n.breaks = 8) +
  scale_x_continuous(name = "Hour", breaks = c(0:23)) +
  labs(title = "Hourly Speed (All Routes)")+
  theme(text = element_text(size = 9))
  
speed_by_route_dir_plot(hourly_route_direction_analytics_cb)

```


### Broad to 7th

```{r}

stop_b7 <- c("SEPTA15796", "SEPTA15908", "SEPTA15798", "SEPTA15907", "SEPTA15799", "SEPTA28699", "SEPTA15800", "SEPTA16966", "SEPTA15814", "SEPTA16965", "SEPTA381", "SEPTA15795", "SEPTA373", "SEPTA15910")

trip_dat_b7 <- (find_trip_dat_v2(apc_data, stop_b7))

analytics_b7 <- analyze_segment(trip_dat_b7)

```


### 7th to Front

```{r}

stop_7f <- c("SEPTA16963", "SEPTA15815", "SEPTA16964", "SEPTA15817","SEPTA15819", "SEPTA16961", "SEPTA32312", "SEPTA16960", "SEPTA15820", "SEPTA16959", "SEPTA15822", "SEPTA15697", "SEPTA15899", "SEPTA15818", "SEPTA16962")

trip_dat_7f <- (find_trip_dat_v2(apc_data, stop_7f))

analytics_7f <- analyze_segment(trip_dat_7f)

```


