---
title: "Olney Corridor Analysis"
author: "Zoe Yoo"
date: "11/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("https://raw.githubusercontent.com/andrewsimpsonphl/transit_segmentation/master/code/segmentation_code.R")

library(rmarkdown)
library(tinytex)
library(tidyverse); library(tidycensus)
library(reactable) ; library(shiny)
library(sf) ; library(sp)
library(tidyverse)
library(rgeos)
library(xlsx)
library(kableExtra)
library(rphl)
library(viridis)
library(gridExtra)
library(scales)

options(tigris_class = "sf") # tells tidycensus to download Census geometries in the sf or Simple Feature format

```


## Overall Corridor Analysis

### Broad Descriptive Stats
* Info on the corridor, which bus routes run through it (18,26), the neighborhood around it, basic population?
Tactors we have: average segment speed, stop spacing (avg_stop_spacing_ft), ons/offs, average load, max entry load (max # of people on first? load), dwell time
* Map of corridor? Automated using leaflet? maybe kind of tricky
* Could use tidycensus to pull in basic descriptive info on the corridor

```{r}
# "NA", SEPTA15796", "SEPTA15908", "SEPTA15798", "SEPTA15907", "SEPTA15799", "SEPTA28699", "SEPTA15800", "SEPTA16966", "SEPTA15814", "SEPTA16965", "SEPTA381","SEPTA15795", "SEPTA373","SEPTA382","SEPTA15910"
# "SEPTA15819", "SEPTA16961", "SEPTA32312", "SEPTA16960", "SEPTA15820", "SEPTA16959", "SEPTA15822", "SEPTA15697", "SEPTA15899", "SEPTA15818", "SEPTA16962", "SEPTA16963" "SEPTA15815" "SEPTA16964" "SEPTA15817" # Olney & 7th to Olney & Front
# "SEPTA372", "SEPTA15911" "NA", "SEPTA15794", "SEPTA15912", "SEPTA15789", "SEPTA15915", "SEPTA15586", "SEPTA15793", "SEPTA15913", "SEPTA15791", "SEPTA15914", "SEPTA15792", "SEPTA15786", "SEPTA15916", "SEPTA15782", "SEPTA15917", "SEPTA15587", "SEPTA16979", "SEPTA15779", "SEPTA15918", "SEPTA15919"


#create_stops()
stops_w_ridership <- st_read("https://github.com/andrewsimpsonphl/transit_segmentation/raw/master/data/stops_ridership.geojson") %>% 
    mutate_if(is.factor, as.character) %>% 
    mutate(route_list = as.list(strsplit(as.character(route_str), ",")))
#create_routes()
routes_w_ridership <- st_read("https://github.com/andrewsimpsonphl/transit_segmentation/raw/master/data/routes_ridership.geojson") %>% 
    mutate_if(is.factor, as.character)
# import links
links <- st_read("https://github.com/andrewsimpsonphl/transit_segmentation/raw/master/data/links_with_stops.geojson")
link_stop_data <- links %>% mutate(fromto = as.character(fromto), secondLocationID = as.character(secondLocationID)) %>% 
    mutate(stop_list = as.list(strsplit(as.character(stop_str), ","))) 
# import APC data
apc_data <- read.csv("./data/combined_apc_dataset.csv") %>%  
    mutate(stop_id = paste0(agency_id, stop_id)) %>% 
    mutate(dwell_time = case_when(
        agency_id == "NJT" ~ dwell_time * 60,
        TRUE ~ dwell_time
    ))

alltracts <- st_read("https://opendata.arcgis.com/datasets/8bc0786524a4486bb3cf0f9862ad0fbf_0.geojson")
#restrict to just tracts that stops are in


#pulling the acs data
acs_trans <- c("B08301_001", #workers
              "B08301_002", #means of transportation to work: car
              "B08301_003", #means of transportation to work: car, drove alone
              "B08301_010", #means of transportation to work: public transit
              "B08301_011", #means of transportation to work: public transit, bus
              "B08301_012", #means of transportation to work: public transit, subway
              "B08301_013", #means of transportation to work: public transit, commuter rail
              "B08301_014", #means of transportation to work: public transit, light rail/trolley
              "B08301_016", #means of transportation to work: taxicab
              "B08301_018", #means of transportation to work: bicycle
              "B08301_019", #means of transportation to work: walked
              "B08301_021" #means of transportation to work: wfh
              )

```

```{r}
# map of routes that exist in this corridor
leaflet()
    addProviderTiles(providers$CartoDB.Positron) %>% 
    addPolylines(data = link_stop_data, color = "#4377bc", weight = 4, layerId = link_stop_data$fromto, opacity = 0.5)
```

### Corridor Level Descriptive Stats

```{r}

```


### Corridor/Route Level Stats


## Sub-Corridor Analysis

* try creating a dataframe of multiple sub-corridors

### Chelten to Broad



### Broad to 7th


### 7th to Front

